---
title: "Stock Data Gathering Functions"
output: github_document
---

### Required packages
- dplyr
- rvest

### Yahoo! Finance

```{r setup, include=FALSE}
library(dplyr)
library(rvest)

source('R/news_links.R')
source('R/stock_news.R')
source('R/sec_financial_docs.R')
source('R/download_sec_filings.R')
```

`news_links` gives the first 15 news links from Apple's stock, AAPL.

```{r}
news.links <- news_links(stock.name = 'aapl')
head(news.links)
```

`stock_news` uses the links acquired from `news_links` to retrieve the text from each news article 

```{r}
aapl.news <- stock_news(stock.links = news.links)
head(summary(aapl.news))
```

### Financial Documents

`sec_financial_docs` returns the links for documents to download. If the keyword does not return a page with the document links, the user is provided with a prompt of options to choose from. Alternatively, you can re-run the function using the desired company name acquired from the printed list.

```{r}
### Use name from 
financial.docs <- sec_financial_docs(company.keywords = 'apple inc', items.per.page = 10)
summary(financial.docs)
```

`download_sec_filings` downloads the documents whose info were acquired using `sec_financial_docs` and stores them into the current working directory

```{r eval = FALSE}
### not run
filinglink <- financial.docs$Filing.Link[[1]]
download_sec_filings(filing.link = filinglink)
```
